---
title: "paper1_figure4"
output:
  html_document: default
  pdf_document: default
bibliography: Hidalgo.bib
---

This reproduces figures from [@RN18]

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```


```{r}
clutch_size<- read.csv("clutch_size.csv")
```

```{r, message=FALSE, warning=FALSE}
ggplot(data=clutch_size)+
  aes(x=RW,y=ClutchSize)+
  geom_point()+
  geom_smooth()+
   labs(y= "Clutch Size", x = "Total Rainfall in Time Window (mm)")+
  theme_bw()
#Hidalgo Aranzamendi N, Hall ML, Kingma SA, van de Pol M, Peters A. Rapid plastic breeding response to rain matches peak prey abundance in a tropical savanna bird. J Anim Ecol. 2019;88:1799–1811. https://doi. org/10.1111/1365-2656.13068

```
Hidalgo Aranzamendi N, Hall ML, Kingma SA, van de Pol M, Peters A. Rapid plastic breeding response to rain matches peak prey abundance in a tropical savanna bird. J Anim Ecol. 2019;88:1799–1811. https://doi. org/10.1111/1365-2656.13068

I recreated figure 4a which is a scatterplot using geom_smooth function to get the rolling mean. The data for this figure was available as an excel spreadsheet but no code was provided. I had to alter the name of one of the columns of the spreadsheet to be able to use it without error in R-studio. I exported the excel spreadsheet into a csv file and read it into R-studio. Despite the fact that the authors did not provide code I was able to successfully recreate the figure. All in all, the process was stragitforward.


References
